Advanced Machine Learning\\Final Report

### 2018-12-23 minutia/AML-report/main.tex
minutia: AML-report bibliography updated and contents added

\documentclass[12pt]{report}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}

@@

@@

\chapter{Proposed and Implemented Method}
Considering this sample-based problem I have picked and implemented a deep reinforcement learning approach, namely Deep Q-Networks (DQN). The elements of this method are explained in the following sections.

This needs to be mentioned that I have examined different method which are excelled in the literature. One of these methods is Deep Deterministic Policy Gradient (DDPG). According

@@

>>>>

\documentclass[12pt]{report}

\usepackage[utf8]{inputenc}

@@

\renewcommand{\bibname}{References}

@@

\chapter{Proposed Methods}
As a problem in which the model (transition probabilities) is not provided, model-free design is what may first come to mind. Different options were available to choose among and each have their own pros and cons. From least squares temporal difference (LSTD) or least squares policy iteration (LSPI) algorithms to more sophisticated one such as asynchronous advantage actor-critic (A3C) \cite{Mnih2016b} are all available

\chapter{Proposed and Implemented Method}
Considering this sample-based problem I have picked and implemented a deep reinforcement learning approach, namely Deep Q-Networks (DQN). DQN is mostly relied on a stabilization technique with neural networks, called Experience replay.
 The elements of this method are explained in the following sections.

This needs to be mentioned that I have examined different method which are excelled in the literature. One of these methods is Deep Deterministic Policy Gradient (DDPG). According to \citet{} such a methods are more applicable to continues action space problems which is not the case here. I have provided a one-to-one comparison chart in Table \ref{tab:dqn vs. ddpg} to discuss particular aspects of these two methods.

\begin{table}
    \centering
    \begin{tabular}{|c|L|L|L|L|}
        \hline
        \textbf{Method}  &    \textbf{Model Dependence}    &   \textbf{Policy Dependence}   &   \textbf{Action Continuity}  & \textbf{Parent Algorithm(s)}\\
        \hline
        \hline
        DQN &   model-free  &   on-policy   &   discrete    &   Q-learning, DL\\
        \hline
        DDPG    &   model-free  &   on-policy   &   continuous  &   Actor-critic\\
        \hline
    \end{tabular}
    \caption{DRL methods comparison chart}
    \label{tab:dqn vs. ddpg}
\end{table}

@@

\bibliographystyle{nips}
\bibliography{library}
